---
title: "Journal (reproducible report)"
author: "Rudan Deng"
date: "2020-11-06"
output:
  html_document:
    toc: true
    toc_float: true
    collapsed: false
    number_sections: true
    toc_depth: 3
    #code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(message=FALSE,warning=FALSE, cache=TRUE)
```

**IMPORTANT:** You can delete everything in here and start fresh. You might want to start by not deleting anything above this line until you know what that stuff is doing.

This is an `.Rmd` file. It is plain text with special features. Any time you write just like this, it will be compiled to normal text in the website. If you put a \# in front of your text, it will create a top level-header.

# Intro to the Tidyverse

Last compiled: `r Sys.Date()`


## Sales by location

Analyze the sales by state:
Which state has the highest revenue?
```{r plot, fig.width=10, fig.height=7}
# We want to analyze the total sales by state (= 1st location). 
# To do it, we have to separate the column location in city, state
# and add the total price (sales price * quantity) to the data.
# 0.0 Load libraries ----
library(tidyverse)
# Excel Files
library(readxl)
# 0.1 Importing Files ----
# A good convention is to use the file name and suffix it with tbl for the data structure tibble
bikes_tbl      <- read_excel(path = "/Users/rudandeng/Documents/05-ICS_Win2020/fund_DS_ws20/DS_101/00_data/01_bike_sales/01_raw_data/bikes.xlsx")
orderlines_tbl <- read_excel("/Users/rudandeng/Documents/05-ICS_Win2020/fund_DS_ws20/DS_101/00_data/01_bike_sales/01_raw_data/orderlines.xlsx")

bikeshops_tbl  <- read_excel("/Users/rudandeng/Documents/05-ICS_Win2020/fund_DS_ws20/DS_101/00_data/01_bike_sales/01_raw_data/bikeshops.xlsx")

# Chaining commands with the pipe and assigning it to order_items_joined_tbl
bike_orderlines_joined_tbl <- orderlines_tbl %>%
        left_join(bikes_tbl, by = c("product.id" = "bike.id")) %>%
        left_join(bikeshops_tbl, by = c("customer.id" = "bikeshop.id"))

# 1.0 Wrangling Data ----
# All actions are chained with the pipe already. 
# You can perform each step separately and use glimpse() or View() to validate your code. 
# Store the result in a variable at the end of the steps.
bike_orderlines_wrangled_tbl <- bike_orderlines_joined_tbl %>%
  # 1.1 Separate location name
  separate(col    = location,
           into   = c("city", "state"),
           sep    = ", ") %>%
  # 1.2 Add the total price (price * quantity) 
  # Add a column to a tibble that uses a formula-style calculation of other columns
  mutate(total.price = price * quantity) %>%
  # 1.3 Optional: Reorganize. Using select to grab or remove unnecessary columns
  # 1.3.1 by exact column name
  select(-...1, -gender) %>%
  
  # 1.3.2 by a pattern
  # You can use the select_helpers to define patterns. 
  # Type ?ends_with and click on Select helpers in the documentation
  select(-ends_with(".id")) %>%
  # 1.3.3 Actually we need the column "order.id". Let's bind it back to the data
  bind_cols(bike_orderlines_joined_tbl %>% select(order.id)) %>%
  
  # 1.3.4 You can reorder the data by selecting the columns in your desired order.
  # You can use select_helpers like contains() or everything()
  select(order.id, contains("order"), contains("model"), contains("category"),
         price, quantity, total.price,
         everything()) %>%
  
  # 1.3.5 Rename columns because we actually wanted underscores instead of the dots
  # (one at the time vs. multiple at once)
  rename(bikeshop = name) %>%
  set_names(names(.) %>% str_replace_all("\\.", "_"))
# 2.0 Business Insights ----
# 2.1 Sales by State ----
# Step 1 - Manipulate
sales_by_state_tbl <- bike_orderlines_wrangled_tbl %>%
  
  # Select columns
  select(state, total_price) %>%
  
  # Grouping by state and summarizing sales
  group_by(state)  %>%
  summarize(sales = sum(total_price)) %>%
  
  # Optional: Add a column that turns the numbers into a currency format 
  # (makes it in the plot optically more appealing)
  # mutate(sales_text = scales::dollar(sales)) <- Works for dollar values
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",",
                                     prefix = " ", 
                                     suffix = " €"))

# 3.1 Sales by State ----

# Step 2 - Visualize
sales_by_state_tbl %>%
  
  # Setup canvas with the columns state (x-axis) and sales (y-axis)
  ggplot(aes(x = state, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding sales to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline
  
  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by State",
    subtitle = "",
    x = "State", # Override defaults for x and y
    y = "Revenue"
  ) +
  # to rotate x-axis labels
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

## Sales by location and year

Analyze the sales by location and year (facet_wrap).
```{r plot_1, fig.width=13, fig.height=7}
# 1.1 Sales by Year ----
library(lubridate)
# Step 1 - Manipulate
sales_by_year_tbl <- bike_orderlines_wrangled_tbl %>%
 
  # Select columns
  select(order_date, total_price) %>%

  # Add year column
  mutate(year = year(order_date)) %>%
 
  # Grouping by year and summarizing sales
  group_by(year) %>% 
  summarize(sales = sum(total_price)) %>%
 
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))

# Step 2 - Visualize
  sales_by_year_tbl %>%
  
  # Setup canvas with the columns year (x-axis) and sales (y-axis)
  ggplot(aes(x = year, y = sales)) +
  
  # Geometries
  geom_col(fill = "#2DC6D6") + # Use geom_col for a bar plot
  geom_label(aes(label = sales_text)) + # Adding labels to the bars
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline

  # Formatting
  # scale_y_continuous(labels = scales::dollar) + # Change the y-axis. 
  # Again, we have to adjust it for euro values
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title    = "Revenue by year",
    subtitle = "Upward Trend",
    x = "", # Override defaults for x and y
    y = "Revenue"
  )
  
  # 1.2 Sales by Year and Location ----
# Step 1 - Manipulate
sales_by_year_state_tbl <- bike_orderlines_wrangled_tbl %>%
 
  # Select columns and add a year
  select(order_date, total_price, state) %>%
  mutate(year = year(order_date)) %>%

  # Group by and summarize year and state
  group_by(year, state) %>%
  summarise(sales = sum(total_price)) %>%
  ungroup() %>%

  # Format $ Text
  mutate(sales_text = scales::dollar(sales, big.mark = ".", 
                                     decimal.mark = ",", 
                                     prefix = "", 
                                     suffix = " €"))
# Step 2 - Visualize
sales_by_year_state_tbl %>%

  # Set up x, y, fill
  ggplot(aes(x = year, y = sales, fill = state)) +

  # Geometries
  geom_col() + # Run up to here to get a stacked bar plot
  geom_smooth(method = "lm", se = FALSE) + # Adding a trendline

  # Facet
  facet_wrap(~ state) +

  # Formatting
  scale_y_continuous(labels = scales::dollar_format(big.mark = ".", 
                                                    decimal.mark = ",", 
                                                    prefix = "", 
                                                    suffix = " €")) +
  labs(
    title = "Revenue by year and location",
    subtitle = "",
    fill = "States" # Changes the legend name
  )

```

# Data Acquisition

## Get Data via API
Get some data via an API. 
Working with Open Notify API, which opens up data on various NASA projects, below presents the peoples who are now in the space.
```{r table_1}
library(httr)
library(jsonlite)

resp <- GET("http://api.open-notify.org/astros.json")
resp
rawToChar(resp$content)
data = fromJSON(rawToChar(resp$content))
names(data)
data$people
```
## MTB Category Price List of Rosebikes

```{r table_2}
# WEBSCRAPING ----

# 1.0 LIBRARIES ----

library(tidyverse) # Main Package - Loads dplyr, purrr, etc.
library(rvest)     # HTML Hacking & Web Scraping
library(xopen)     # Quickly opening URLs
library(jsonlite)  # converts JSON files to R objects
library(glue)      # concatenate strings
library(stringi)   # character string/text processing

# 1.1 COLLECT PRODUCT PRICE OF MTB CATEGORY ----

url_mtb          <- "https://www.rosebikes.de/fahrräder/mtb"

# Read in the HTML for the MTB category
html_home         <- read_html(url_mtb)

bike_family_tbl <- html_home %>%
  
# Get the nodes for the MTB category
  html_nodes(css = ".catalog-category-bikes__button") %>%
  html_attr("href") %>%
  enframe(name = "position", value = "product_url") %>%
  mutate(
    url = glue("https://www.rosebikes.de{product_url}"))%>%
  distinct(url)

# get the bike name  
  get_bike_data <- function(a) {
  html_bike_mtb  <- read_html(a)
  
  bike_url_tbl        <- html_bike_mtb %>%
    html_nodes(css = ".catalog-category-model__title") %>%
    html_text() %>%   
    stringr::str_replace_all(pattern = "\\\n", replacement = "")%>%
    enframe(name = "position", value = "bike_name")
}

bike_category_url_vec <- bike_family_tbl$url

bike_data_lst <- map(bike_category_url_vec, get_bike_data)
bike_data_tbl <- bind_rows(bike_data_lst) 

# get the bike price
  
  get_bike_price <- function(b) {
  html_bike_mtb  <- read_html(b)
  
  bike_url_tbl        <- html_bike_mtb %>%
    html_nodes(css = ".catalog-category-model__price-current-value") %>%
  html_text() %>%   
  stringr::str_replace_all(pattern = "\\\n", replacement = "")%>%
    enframe(name = "position", value = "bike_price")
}

bike_category_url_vec <- bike_family_tbl$url

bike_price_lst <- map(bike_category_url_vec, get_bike_price)
bike_price_tbl <- bind_rows(bike_price_lst) 

bike_mtb_tbl <- left_join(bike_data_tbl, bike_price_tbl)
bike_mtb_tbl

```


# Adding R stuff

So far this is just a blog where you can write in plain text and serve your writing to a webpage. One of the main purposes of this lab journal is to record your progress learning R. The reason I am asking you to use this process is because you can both make a website, and a lab journal, and learn R all in R-studio. This makes everything really convenient and in the same place. 

So, let's say you are learning how to make a histogram in R. For example, maybe you want to sample 100 numbers from a normal distribution with mean = 0, and standard deviation = 1, and then you want to plot a histogram. You can do this right here by using an r code block, like this:


```{r, eval = TRUE}
numbers <- 1:1000

# This will print the first 10 elements of the vector numbers
numbers[1:10]

# This will plot a histogram of 100 random elements of the vector numbers
hist(sample(numbers, 100, replace = T))
```


When you knit this R Markdown document, you will see that the histogram is printed to the page, along with the R code. This document can be set up to hide the R code in the webpage, just delete the comment (hashtag) from the cold folding option in the yaml header up top. For purposes of letting yourself see the code, and me see the code, best to keep it the way that it is. You'll learn that all of these things and more can be customized in each R code block.